Crop adaptation through gene flow

### 2016-06-28 Crop_adaptation_gene_flow_gj_outline_shortened.tex
Update Crop_adaptation_gene_flow_gj_outline_shortened.tex

>>>>

There are two types of cultivated coconut (Pacific and Indian/Atlantic), corresponding to two separate domestications, with a history of human-facilitated admixture between them \cite{gunn2011independent}\.
[[See cited references in intro of "Population Genetics, Lethal Yellowing Disease, and Relationships among Mexican and
Imported Coconut Ecotypes"]]
